---
title: "Unsupervised Smooth Contour Line Detection for images"
author: "Jan Wijffels"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Unsupervised Smooth Contour Line Detection for images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The  **image.ContourDetector** R package implements Unsupervised Smooth Contour Line Detection for images.

- It contains 1 main function **image_contour_detector**. If you give it an image matrix with grey scale values in the 0-255 range, it will find contour lines in the image.
- The algorithm is defined in Rafael Grompone von Gioi, and Gregory Randall, Unsupervised Smooth Contour Detection, Image Processing On Line, 6 (2016), pp. 233-267. https://doi.org/10.5201/ipol.2016.175


## Examples

Read in an image with values in the 0-255 range (pgm image: http://netpbm.sourceforge.net/doc/pgm.html)

```{r}
library(image.ContourDetector)
library(pixmap)
imagelocation <- system.file("extdata", "image.pgm", package="image.ContourDetector")
image <- read.pnm(file = imagelocation, cellres = 1)
x <- image@grey * 255
contourlines <- image_contour_detector(x)
contourlines
par(mai = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(image)
plot(contourlines, add = TRUE, col = "red")
```

If you have another type of image (jpg, png, ...). Convert the image to pgm format before getting the 0-255 range or convert it to grey format before passing it on to the function.

```{r}
library(magick)
f <- tempfile(fileext = ".pgm")
x <- image_read(system.file("extdata", "atomium.jpg", package="image.ContourDetector"))
x <- image_convert(x, format = "pgm", depth = 8)
image_write(x, path = f, format = "pgm")

image <- read.pnm(file = f, cellres = 1)
contourlines <- image_contour_detector(image@grey * 255)
contourlines
par(mfrow = c(1, 2), mai = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(image)
plot(contourlines, add = TRUE, col = "red", lwd = 2)
plot(contourlines)
```

## Support in image recognition

Need support in image recognition?
Contact BNOSAC: http://www.bnosac.be


